Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-09 authorinstr_2.tex
Wat userclassification toegevoegd.

\subsubsection{Usecase: Predicting Political Preferences}
During election time 
\subsection{Tag based analysis}

>>>>

\subsubsection{Usecase: Predicting Political Preferences}
During election time it can be useful to predict the political preferences of a user. In \cite{pol} a solution to this problem is presented. As not all tweets from users reflect their political preference a preprocessing of data is done in order to filter the tweets.

To achieve this a combination of (political) hashtags in combination with twitter activities is used. To know if a user mentions an account of an election candidate \cite{pol} semi-automatically scraped a number of these accounts. Furthermore they collected 181972 tweets about politics, before processing these tweets non-personal and spam accounts had to be filtered. 
\subsection{Tag based analysis}
